%-------------------------
% ___CV FOR ACADEMICS___
% Author : Aditya Wagh
% File Name : aditya_cv.tex
% Date Modified : 01/06/2019
%------------------------


\documentclass[a4paper]{article}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames,x11names]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
%\usepackage{tfrupee}  % for rupee symbol (use \rupee~)
%\usepackage{multicol} % for multi column in header
\usepackage{xcolor}
\usepackage{vwcol}
\usepackage{ragged2e}  % for justifying text
\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000
%\usepackage[empty]{fullpage}
%otherwise
\usepackage[paper=letterpaper,
top=21.1mm,
bottom=21.1mm,
right=21.1mm,
left=23.1mm
]{geometry}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\colorlet{varHeadingColor}{RoyalBlue}


% Sections formatting
\titleformat{\section}{ 
		 \vspace{-7pt}\raggedright\large \sffamily \color{varHeadingColor}
}{}{0em}{}[\color{varHeadingColor}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{ #2 \vspace{-5pt}}
	}
}

\newcommand{\resumeSubheadingEducation}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{\normalsize#1} & {\normalsize #2} \\
		\textit{\small #3} & \textit{\small #4}\\
		%		\textit{\small #5} \\
		% 		\textit{\small#6} \\
		% 		\textit{\small#7} \\
		% 		\textit{\small#8} \\
	\end{tabular*}
}

% \newcommand{\resumeSubheading}[4]{
% 	\vspace{-1pt}\item
% 	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
% 		\textbf{\normalsize #1} & {\normalsize #2} \\
% 		\textit{\small#3} & \textit{\small #4} \\
% 	\end{tabular*}
% 	\smallskip \\
% }
\newcommand{\resumeSubheading}[2]{
	\vspace{-1pt}\item
	{\textbf{\noindent #1}} \hfill {#2} \\
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{0pt}}
\newcommand{\resumeSubItemOneArg}[1]{\item \small #1\vspace{-1pt}}

\renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemiii}{$\cdot$}


\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize} \vspace*{-5pt}}
	\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{{\Large \color{varHeadingColor} Aditya Wagh}} & {\color{varHeadingColor}Email} : \href{mailto:aditya@adityawagh.ml}{aditya@adityawagh.ml}\\
    \href{http://adityawagh.ml/}{http://www.adityawagh.ml} & {\color{varHeadingColor}Phone} : +91-74477-93555 \\
\end{tabular*}

\vspace{-2pt}
%  EDUCATION

\section{Education}
\justifying
\resumeSubHeadingListStart
\resumeSubheadingEducation
{Birla Institute of Technology and Science (BITS), Pilani}{\textbf{Pilani, India}}
{Bachelor of Engineering with Honors in Electronics and Instrumentation, {\small \emph{GPA}: 5.55/10} \vspace{1pt}}  {Aug 2015 -- Jul 2019} \vspace{1pt} \\
{\justifying \small \emph{\underline{Relevant coursework}}: Computer Programming,  Discrete Mathematics, Neural Networks, Computer Architecture, Microprocessors \& Interfacing, Data Communication \& Networks, Digital Signal Processing, Control Systems, Mechanics, Probability \& Statistics, Linear Algebra}

\vspace{-5pt}
\resumeSubheadingEducation
{LVH Arts, Science \& Commerce College}{\textbf{Nashik, India}}
{Higher Secondary Ceritificate, MSBSHSE, {\small \emph{Marks}: 85.69\%} \vspace{1pt} }  {Aug 2013 -- June 2015}
\vspace{-5pt}
\resumeSubheadingEducation
{Symbiosis School}{\textbf{Nashik, India}}
{All India Secondary School Examination, CBSE, {\small \emph{GPA}: 10/10} \vspace{1pt}}  {Jun 2009 -- May 2013}

\vspace{-8pt}
\resumeSubHeadingListEnd

%  TECHNICAL SKILLS

\section{Technical Proficiency}
\justifying
\resumeSubHeadingListStart
\resumeSubItem{Development Languages}
{Python, C, C++, MATLAB, Shell, \LaTeX, HTML, CSS, JavaScript}
\resumeSubItem{Tools, Frameworks and Libraries}
{Keras, TensorFlow, PyTorch, OpenCV, MATLAB, Simulink, LabVIEW, Bootstrap, Git}
\resumeSubHeadingListEnd


% RESEARCH EXPERIENCE

\section{Work Experience}
\justifying
\resumeSubHeadingListStart
\resumeSubheading
{Research Assistant, Central Electronics Engineering Research Institute, Pilani}{Jul 2018 -- Dec 2018}
%\vspace{2pt} \\
\emph{Project}: Detection of faulty power transmission lines from aerial images using Mask R-CNN
\resumeItemListStart
\resumeSubItemOneArg{Reviewed and compared the state-of-the-art instance segmentation models for aerial images.}
\resumeSubItemOneArg{Improved mAP by 4.31 over other existing models using salience biased loss function with the \textbf{Mask RCNN} architecture.}
\resumeSubItemOneArg{Contributed in development of software pipeline to annotate 8000+ Infrared and RBD images TV-L power-line dataset.}
\resumeItemListEnd
\vspace{-5pt}
\resumeSubheading
{Software Intern, Apras Polymers \& Engineering Co.Pvt. Ltd, Nashik}{May 2018 -- Jul 2018}
%\vspace{2pt} \\
\emph{Project}: A Business2Consumer website using Bootstrap and Jekyll.
\resumeItemListStart
\resumeSubItemOneArg{Created the UI of the website using the \textbf{Figma tool} and developed the front end using the \textbf{Bootstrap} CSS framework.}
\resumeSubItemOneArg{Generated the skeleton of the website using \textbf{HTML} and \textbf{Jekyll v4} and animated the components using \textbf{animate.css}}
\resumeItemListEnd
\vspace{-5pt}
\resumeSubheading
{Software Intern, The Ramco Cements Ltd, Jaggayapeta}{May 2017 -- Jul 2017}
%\vspace{2pt} \\
\emph{Project}: Design of a Inventory Management Web application for the Plant
\resumeItemListStart
\resumeSubItemOneArg{Designed the UI of the portal using the \textbf{Figma tool} and wrote the front end using \textbf{.NET}(ASP.NET and VB.NET)}
\resumeSubItemOneArg{Designed a relational database to store inventory details using \textbf{Microsoft SQL Server}.}

	\vspace{-5pt}
\resumeSubHeadingListEnd
\resumeSubHeadingListEnd
\vspace{-5pt}
% PROJECTS

\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Oriented Object Detection on Aerial Images}{
    \resumeItemListStart
     \resumeSubItemOneArg{Researched object detection methods for oriented text detection}
      \resumeSubItemOneArg{Achieved around 65 mAP on the DOTA dataset by transfer learning on the R2CNN model.}
       \resumeItemListEnd
}
\resumeSubItem{Variable Computation in Recurrent Neural Networks}{
    \resumeItemListStart
    \resumeSubItemOneArg{Modified a RNN model to make it learn to vary the amount of computation according to the sequence that they process.}
    \resumeSubItemOneArg{Implemented a scheduler for the RNN unit which decides the computation required at the current timestep.}
    \resumeSubItemOneArg{Reduced the number of operations for bit-level language modelling to around 50\% compared to normal RNN unit.}
    \resumeItemListEnd
    \vspace{-5pt}

% \resumeSubItem{Microphone Signal Conditioning System (2017)}{
%     \resumeItemListStart
%      \resumeSubItemOneArg{Designed a signal conditioning circuit for a microphone using OPAMPS.}
%       \resumeSubItemOneArg{Utilised the condenser microphone as a capacitance in the RC Filter Circuit. }
%       \resumeSubItemOneArg{Interfaced the circuit with the computer using NI-DAQmx data acquisition card and interpreted noisy signals in LabVIEW.}
%       \resumeItemListEnd
% }

\resumeSubItem{RISC Processor Design using HDL}{
\resumeItemListStart
    \resumeSubItemOneArg{Designed, programmed and tested 16-bit multi-cycle processor for a given set of instructions and constraints.}
    \resumeSubItemOneArg{Followed modular approach for programming the processor and its test bench, by dividing it into sub-modules such
as memory, register file, ALU and control unit. }
\resumeItemListEnd
}

\resumeSubItem{Finite Impulse Response filter design using an adjustable window filter}{
      \resumeItemListStart
      \resumeSubItemOneArg{Implemented an adjustable window function based on the combination of Blackman and Lanczos window.}
      \resumeSubItemOneArg{Achieved a 75\% better side-lobe roll off ratio than Lanczos window.}
      \resumeItemListEnd
    }
}

% \vspace{-5pt}
\resumeSubHeadingListEnd


%-------------------------------------------

% 	%
% 	%--------RELEVANT COURSES AND ELECTIVES------------
% 	\section{Relevant courses and Electives}
% 	Digital Design $\cdot$ Microprocessors and Interfacing $\cdot$ Computer Programming $\cdot$ Computer Architecture $\cdot$ Operating Systems $\cdot$ Analog \& Digital VLSI Design $\cdot$  Neural Networks \& Fuzzy Logic $\cdot$ Digital Signal Processing 
% 	%-------------------------------------------

%
%--------POSITIONS OF RESPONSIBILITY----------
\section{Volunteer Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Vice-Chairperson, IEEE Student Branch, BITS Pilani}{Jul 2017 - May 2018}
\resumeItemListStart \vspace{-12pt}
\resumeSubItemOneArg{Promoted IEEE Student memberships by 30\% in the campus by organising membership drives, workshops and technical events}
% 	\resumeSubItemOneArg{Increased the participation in all the events organized by more than 40 percent than last few years.}
\resumeSubItemOneArg{Responsible for setting up the IEEE hosted website for the chapter and IEEE Insight, the monthly newsletter of the chapter.}
\resumeSubItemOneArg{Revamped the organisational hierarchy of the chapter, introducing various managerial and technical posts.}
\resumeItemListEnd
	\vspace{-5pt}
\resumeSubheading
{Governing Council Member, Society for Students Mess Services, BITS Pilani}{Aug 2018 - July 2019}
\resumeItemListStart \vspace{-12pt}
\resumeSubItemOneArg{\textbf{Mess Representative:} Responsible for sanctioning leaves of the workers, collecting feedback and taking necessary actions.}
\resumeSubItemOneArg{\textbf{QHSE:}}{Drafted a QHSE framework for SSMS activities and conducted regular audits every semester.}
\resumeSubItemOneArg{\textbf{HR:}}{Responsible for performance appraisals, providing education/medical loans and  managing internal worker conflicts.}
\resumeItemListEnd

\resumeSubHeadingListEnd
%	%-------------------------------------------

% CCERTIFICATIONS

% \section{Certifications}

% \justifying
% \resumeSubHeadingListStart

% \resumeSubItem{\href{https://students.codingninjas.com/verify/0e0427a922f32cf0}{Introduction to Python}}
% {\hfill{Coding Ninjas}}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \resumeSubItem{\href{https://www.coursera.org/account/accomplishments/certificate/PERFF99LL8T7}{Mathematics for Machine Learning}}
% {\hfill{University College London (UCL), Coursera}}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \resumeSubItem{\href{https://www.coursera.org/account/accomplishments/certificate/KJBZ3XKKYAXM}{Deep Learning}}
% {\hfill{deeplearning.ai, Coursera}}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \resumeSubItem{\href{https://www.coursera.org/account/accomplishments/certificate/7G4V3W8T4J7L}{Introduction to TensorFlow for Artificial Intelligence, Machine Learning, and Deep Learning}}
% {\hfill{deeplearning.ai, Coursera}}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \resumeSubItem{\href{https://www.coursera.org/account/accomplishments/certificate/HHUQBSMH53JY}{Convolutional Neural Networks in TensorFlow}}
% {\hfill{deeplearning.ai, Coursera}}
% \resumeSubHeadingListEnd

\section{MOOCs \& Certifications}

\justifying

{\href{https://students.codingninjas.com/verify/0e0427a922f32cf0}{{\textbf{Introduction to Python}}}(Coding Ninjas)}; {\href{https://www.coursera.org/account/accomplishments/certificate/PERFF99LL8T7}{\textbf{Mathematics for Machine Learning}}(Coursera)};{\textbf{Machine Learning}}[Audit](Coursera)}; {\href{https://www.coursera.org/account/accomplishments/certificate/KJBZ3XKKYAXM}{\textbf{Deep Learning}}(Coursera)}; {\href{https://www.coursera.org/account/accomplishments/certificate/7G4V3W8T4J7L}{\textbf{Introduction to TensorFlow}}(Coursera)}; {\href{https://www.coursera.org/account/accomplishments/certificate/HHUQBSMH53JY}{\textbf{Convolutional Neural Networks in TensorFlow}}(Coursera)}

\end{document}
